---
title: "Staggregate Figure"
output: html_document
date: "2022-10-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load Packages
```{r}
library(stagg)
library(tidyverse)
library(here)
library(raster)
library(sf)
library(gridExtra)
library(tigris)
library(ggpubr)
library(data.table)
library(shades)
```

Read in Data
```{r}
# Raster brick 1 year of temp data !!!This file is to big for the repo, you must have it in your local data folder!!!
data <- crop(brick(here("data", "era5_temp_2020.nc")), c((360 + (x_min - .5)), 360 + (x_max + .5), (y_min - .5), (y_max + .5)))

# Converting to C
data <- data -273.15


# Select counties in CA
ca_counties <- st_crop(counties("CA"), c(xmin = x_min, xmax = x_max, ymin = y_min, ymax = y_max)) %>%
  filter(GEOID %in% c("06003", "06109", "06043", "06009")) %>% 
  st_as_sf()
```

Define Variables
```{r, include = FALSE}
# Cropping and Placement
state_abb <- "CA"
counties_geoid <- c("06107", "")
x_min <- -121
y_min <- 37
x_max <- x_min + 2
y_max <- y_min + 2
y_int <- .1

fill_palette <- "Spectral"

```


Define Rotation Functions (This Code is Not My Own, I don't understand it very well)
```{r}
rotate_data <- function(data, x_add = 0, y_add = 0) {
  
  # shear_matrix <- function(){ matrix(c(1,1,1,1), 2, 2) }
  shear_matrix <- function(){ matrix(c(2, 1.2, 0, 1), 2, 2) }
  # rotate_matrix <- function(x){ 
  #   matrix(c(1,1,1,1), 2, 2) 
  # }
  
  rotate_matrix <- function(x){
    matrix(c(cos(x), sin(x), -sin(x), cos(x)), 2, 2)
  }
  data %>% 
    dplyr::mutate(
      geometry = .$geometry * shear_matrix() * rotate_matrix(pi/20) + c(x_add, y_add)
    )
}

rotate_data_geom <- function(data, x_add = 0, y_add = 0) {
  shear_matrix <- function(){ matrix(c(2, 1.2, 0, 1), 2, 2) }
  
  rotate_matrix <- function(x) { 
    matrix(c(cos(x), sin(x), -sin(x), cos(x)), 2, 2) 
  }
  data %>% 
    dplyr::mutate(
      geom = .$geom * shear_matrix() * rotate_matrix(pi/20) + c(x_add, y_add)
    )
}
```


Create Hourly Raster Brick
```{r}
# Blank Plot
hourly <- ggplot()

# While Loop to Keep Adding Layers to Plot
i <- 10 # Choosing to start at layer 10 because it looks a bit like the daily aggregation
while(i <= 28){
  
  # Read layer from data
  a <- raster(data, layer = i) %>% 
    rasterToPolygons(na.rm = TRUE) %>% 
    st_as_sf() %>% 
    rename(value = 1) %>% 
    st_as_sf()
  
  hourly <- hourly + 
    geom_sf(data = a %>% rotate_data(y_add = y_int*i), mapping = aes(fill = value), size = 2, color = "black") +
    geom_sf(data = a %>% rotate_data(y_add = y_int*i), mapping = aes(fill = value), size = 0)
  i = i + 1
}

```



Polish Hourly Raster Brick
```{r}
hourly <- hourly +
  scale_fill_distiller(palette = fill_palette, direction = -1)
  labs(y = "\U2190 Hours \U2192",
       caption = "Hourly Gridded Data") +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        legend.position = "none",
        plot.caption = element_text(size = 20, face = "plain", hjust = .5),
        plot.background = element_blank(),
        panel.background = element_blank())

hourly
```



Create Daily Raster Brick
```{r}
# Generate daily raster brick (taken from stagg)
indices <- rep(1:(raster::nlayers(data)/24),each=24)
clim_daily <- raster::stackApply(data, indices = indices, fun=mean)

# Empty Plot
daily <- ggplot()

# While Loop to Keep Adding Layers to Plot
i <- 1
while(i <= 6){
  
  # Read layer from data
  a <- raster(clim_daily, layer = i) %>% 
    rasterToPolygons(na.rm = TRUE) %>% 
    st_as_sf() %>% 
    rename(value = 1) %>% 
    st_as_sf()
  
  # Spacing out the layers a little more by doing 3*y_int*i
  daily <- daily + 
    geom_sf(data = a %>% rotate_data(y_add = 3*y_int*i), mapping = aes(fill = value), size = 2, color = "black") +
    geom_sf(data = a %>% rotate_data(y_add = 3*y_int*i), mapping = aes(fill = value), size = 0)
  i = i + 1
}

```


Polish Daily Raster Brick
```{r}
daily <- daily +
  scale_fill_distiller(palette = fill_palette, direction = -1) +
  labs(y = "\U2190 Days \U2192",
       caption = "Daily Gridded Data") +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        legend.position = "none",
        plot.caption = element_text(size = 20, face = "plain", hjust = .5),
        plot.background = element_blank(),
        panel.background = element_blank())

daily
```


Create Transformed Raster Brick
```{r}
clim_daily_sq <- clim_daily ^ 2

daily_sq <- ggplot()

# While Loop to Keep Adding Layers to Plot
i <- 1
while(i <= 6){
  
  # Read layer from data
  a <- raster(clim_daily_sq, layer = i) %>% 
    rasterToPolygons(na.rm = TRUE) %>% 
    st_as_sf() %>% 
    rename(value = 1) %>% 
    st_as_sf()
  
  daily_sq <- daily_sq + 
    geom_sf(data = a %>% rotate_data(y_add = 3*y_int*i), mapping = aes(fill = value), size = 2, color = "black") +
    geom_sf(data = a %>% rotate_data(y_add = 3*y_int*i), mapping = aes(fill = value), size = 0)
  i = i + 1
}




```

Polish Transformed Raster Bricks
```{r}
daily_1 <- daily +
  theme(plot.caption = element_text(face = "plain")) +
  labs(caption = "X") +
  theme(plot.caption = element_text(size = 12))

daily_sq <- daily_sq +
  scale_fill_distiller(palette = fill_palette, direction = -1) +
  labs(caption = expression("X"^{2}),
       y = "") +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        legend.position = "none",
        plot.caption = element_text(size = 12, hjust = .5),
        plot.background = element_blank(),
        panel.background = element_blank())


daily_1
daily_sq
```

Aggregate by Day/Month/Year
```{r}
# Manually generate table of grid cells to turn into polygons (overlay_weights doesn't like using ERA5 grid as polygons)
x_pos <- ((4.0*(360+ x_min-.5)):(4.0*(360 + x_max+.5) - 1)) / 4.0 # Vector of x positions
y_pos <- ((4.0*(y_min-.5)):(4.0*(y_max+.5) - 1)) / 4.0 # Vector of y positions

y_all <- sort((rep(y_pos, each = length(x_pos))), decreasing = TRUE) # Repeating each y position by length of x_pos

x_all <- c() # Repeating vector x_pos by length of y_pos
i <- length(y_pos)
while(i >= 1){
  x_all <- c(x_all, x_pos)
  i = i - 1
}

grid_polys <- rasterToPolygons(crop(raster(era5_grid), c(360 +x_min-.5, 360 +x_max+.5, y_min-.5, y_max+.5))) %>% 
  st_as_sf() %>% 
  mutate(poly_id = as.character(1001:(length(x_all) + 1000))) %>% 
  st_as_sf() 




overlay_grid <- data.table(data.frame(x = x_all, 
                           y = y_all,
                           poly_id = as.character(1001:(length(x_all) + 1000)),
                           w_area = 1,
                           w_sum = 1)) # Putting it all together in an sf object representing our ERA5 grid

# Get aggregated weights
agged_grid <- staggregate_polynomial(data = data, overlay_weights = overlay_grid, daily_agg = "average", time_agg = "month", degree = 2)

# Divide by Number of Days
agged_grid[, ':=' (order_1 = ifelse(month == 2, order_1 / 29, order_1 / 31),
                   order_2 = ifelse(month == 2, order_2 / 29, order_2 / 31))]

# Run a while loop to separate "X" layers by months and add each to a plot
monthly_gridded_1 <- ggplot()

i <- 3
while(i >= 1){
  a <- agged_grid %>% 
    data.frame() %>% 
    filter(month == i) %>% 
    dplyr::select(poly_id, order_1) %>% 
    inner_join(grid_polys, by = "poly_id") %>% 
    st_as_sf()
  
  monthly_gridded_1 <- monthly_gridded_1 + 
    geom_sf(data = a %>% rotate_data(y_add = 10*y_int*(4 - i)), mapping = aes(fill = order_1), size = 2, color = "black") +
    geom_sf(data = a %>% rotate_data(y_add = 10*y_int*(4 - i)), mapping = aes(fill = order_1), size = 0)
  
  i = i - 1
}

# Run a while loop to separate "X^2" layers by months and add each to a plot
monthly_gridded_2 <- ggplot()

i <- 3
while(i >= 1){
  a <- agged_grid %>% 
    data.frame() %>% 
    filter(month == i) %>% 
    dplyr::select(poly_id, order_2) %>% 
    inner_join(grid_polys, by = "poly_id") %>% 
    st_as_sf()
  
  monthly_gridded_2 <- monthly_gridded_2 + 
    geom_sf(data = a %>% rotate_data(y_add = 10*y_int*(4 - i)), mapping = aes(fill = order_2), size = 2, color = "black") +
    geom_sf(data = a %>% rotate_data(y_add = 10*y_int*(4 - i)), mapping = aes(fill = order_2), size = 0)
  
  i = i - 1
}

```

Polish Monthly Gridded Brick
```{r}
monthly_gridded_1 <- monthly_gridded_1 +
  scale_fill_distiller(palette = fill_palette, direction = -1) +
  labs(y = "\U2190 Days / Months / Years \U2192",
       caption = "X") +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        legend.position = "none",
        plot.caption = element_text(size = 12, face = "plain", hjust = .5),
        plot.background = element_blank(),
        panel.background = element_blank())

monthly_gridded_2 <- monthly_gridded_2 +
  scale_fill_distiller(palette = fill_palette, direction = -1)  +
  labs(caption = expression("X"^{2}),
       y = "") +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        legend.position = "none",
        plot.caption = element_text(size = 12, hjust = .5),
        plot.background = element_blank(),
        panel.background = element_blank())



monthly_gridded_1
monthly_gridded_2

```


Aggregate by Polygon
```{r}

# Get overlay weights
overlay <- overlay_weights(ca_counties, "GEOID")

# Get aggregated weights
agged_data <- staggregate_polynomial(data = data, overlay_weights = overlay, daily_agg = "average", time_agg = "month", degree = 2)

# Divide by Number of Days
agged_data[, ':=' (order_1 = ifelse(month == 2, order_1 / 29, order_1 / 31),
                   order_2 = ifelse(month == 2, order_2 / 29, order_2 / 31))]

# Run a while loop to separate "X" layers by months and add each to a plot
monthly_county_1 <- ggplot()

i <- 3
while(i >= 1){
  a <- agged_data %>% 
    data.frame() %>% 
    filter(month == i) %>% 
    dplyr::select(poly_id, order_1) %>% 
    rename(GEOID = poly_id) %>% 
    inner_join(ca_counties, by = "GEOID") %>% 
    st_as_sf()  
  
  box <- st_make_grid(a, n = 1) %>% 
    data.frame() %>% 
    st_as_sf() %>% 
    rotate_data(y_add = 10*y_int*(4 - i))
  
  a <- a %>% 
    rotate_data(y_add = 10*y_int*(4 - i))
  
  
  
  monthly_county_1 <- monthly_county_1 +
    geom_sf(data = box, size = 1, color = "grey", fill = "white") +
    geom_sf(data = a, mapping = aes(fill = order_1), size = 2, color = "black") +
    geom_sf(data = a, mapping = aes(fill = order_1), size = 0)
  
  i = i - 1
}


monthly_county_2 <- ggplot()

i <- 3
while(i >= 1){
  a <- agged_data %>% 
    data.frame() %>% 
    filter(month == i) %>% 
    dplyr::select(poly_id, order_2) %>% 
    rename(GEOID = poly_id) %>% 
    inner_join(ca_counties, by = "GEOID") %>% 
    st_as_sf()
  
   box <- st_make_grid(a, n = 1) %>% 
    data.frame() %>% 
    st_as_sf() %>% 
    rotate_data(y_add = 10*y_int*(4 - i))
  
  a <- a %>% 
    rotate_data(y_add = 10*y_int*(4 - i))
  
  monthly_county_2 <- monthly_county_2 + 
     geom_sf(data = box, size = 1, color = "grey", fill = "white") +
    geom_sf(data = a, mapping = aes(fill = order_2), size = 2, color = "black") +
    geom_sf(data = a, mapping = aes(fill = order_2), size = 0)
  
  i = i - 1
}
```

Polish Monthly Polygon Brick
```{r}
monthly_county_1 <- monthly_county_1 +
  scale_fill_distiller(palette = fill_palette, direction = -1) +
  labs(y = "\U2190 Days / Months / Years \U2192",
       caption = "X") +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        legend.position = "none",
        plot.caption = element_text(size = 12, face = "plain", hjust = .5),
        plot.background = element_blank(),
        panel.background = element_blank())

monthly_county_2 <- monthly_county_2 +
  scale_fill_distiller(palette = fill_palette, direction = -1) +
  labs(caption = expression("X"^{2}),
       y = "") +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.line = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 16),
        legend.position = "none",
        plot.caption = element_text(size = 12, hjust = .5),
        plot.background = element_blank(),
        panel.background = element_blank())

monthly_county_1
monthly_county_2
```
